---
title: "R Notebook"
output: html_notebook
---



首先需要手动输入钠含量，把盐摄入单独列出来。把脂肪酸含量数据加进去。

```{r}
library(tidyverse)
fatty2002 <- read.csv("data/fatty2002.csv",stringsAsFactors = F)
fatty2002 <- fatty2002 %>% dplyr::select(-FD_name)
fatty2002[is.na(fatty2002)] <- 0

fatty2004 <- read.csv("data/fatty2004.csv",stringsAsFactors = F)
fatty2004 <- fatty2004 %>% dplyr::select(-FD_name)
fatty2004[is.na(fatty2004)] <- 0
```
*CMFP index 计算方法*
在原有28个food group基础上重新计算各个component的得分：
1. Grain:fg1,fg2,fg4,fg5, fg6??
2. Vegetable:fg10, fg11
3. Fruits:fg12, fg13
4. Dairy:fg21
5. Beans:fg7, fg8, fg20
6. Meat and Poutry:fg14-fg17
7. Fish and shrimp:fg19
8. Eggs:fg18
9. Fats and oils:27
10.Salt:fg28-需要重新计算
Dietary intakes were adjusted for total energy intake using density method and standardized to 2000 kcal. Intakes between minimum and maximum levels were scored proportionately.

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
