---
title: "R Notebook"
output: html_notebook
---

首先需要手动输入钠含量，把盐摄入单独列出来。把脂肪酸含量数据加进去。

```{r import dataset}
library(tidyverse)
fatty2002 <- read.csv("data/fatty2002.csv",stringsAsFactors = F)
fatty2002 <- fatty2002 %>% dplyr::select(-FD_name)
fatty2002[is.na(fatty2002)] <- 0

fatty2004 <- read.csv("data/fatty2004.csv",stringsAsFactors = F)
fatty2004 <- fatty2004 %>% dplyr::select(-FD_name)
fatty2004[is.na(fatty2004)] <- 0

fct2002 <- read.csv("data/fct2002.csv",stringsAsFactors = F)
fct2002 <- fct2002 %>% dplyr::select(-FD_name)
fct2002 <- left_join(fct2002,fatty2002,by="Fcode")
fct2002[is.na(fct2002)] <- 0

fct2004 <- read.csv("data/fct2004.csv",stringsAsFactors = F)
fct2004 <- fct2004 %>% dplyr::select(-FD_name)
fct2004 <- left_join(fct2004,fatty2004,by="Fcode")
fct2004[is.na(fct2004)] <- 0

fct_all <- rbind(fct2002,fct2004)
fct_all <- dplyr::rename(fct_all,foodcode=Fcode)
write.csv(fct_all,"chns/fct_all.csv",row.names = F)
```


```{r}
nutr1 <- read.csv("chns/NUTR1_00.csv",stringsAsFactors = F)
nutr3 <- read.csv("chns/NUTR3_00.csv",stringsAsFactors = F)
```



```{r}
fg2004 <- read.csv("data/fg2004.csv",stringsAsFactors = F)
fg2004 <- fg2004 %>% dplyr::mutate(fg_fiber=(amt*edible)/100*(fiber/100),fg_na=(amt*edible)/100*(sodium/100),fg_pufa=(amt*edible)/100*(PUFA/100),fg_n3=(amt*edible)/100*((EPA+DHA)*Total/100))
```

*CMFP index 计算方法*
在原有28个food group基础上重新计算各个component的得分：
1. Grain:谷物
2. Vegetable:fg10, fg11
3. Fruits:fg12, fg13
4. Dairy:fg21
5. Beans:大豆及其制品
6. Meat and Poutry:fg14-fg17
7. Fish and shrimp:fg19
8. Eggs:fg18
9. Fats and oils:27
10.Salt:fg28-需要重新计算

Dietary intakes were adjusted for total energy intake using density method and standardized to 2000 kcal. Intakes between minimum and maximum levels were scored proportionately.

*Dash 计算方法*
1. grain:6 serving, 28 gram
2. vegetables: 80g
3. fruit: 80g
4. dairy: 245g; 
5. meat, poultry and fish: 28g; 
6. eggs: 50g; 
7. nuts: 43g; 
8. seeds: 28g; 
9. legumes: 113g; 
10. fats and oils: 15g
11. Sweets,added sugars: sweets:15g,5/week
12. SSSB:<=5/week=10 >=7/week=0
13. sodium：

Serving size: vegetables and fruit: 80g; dairy: 245g; meat, poultry and fish: 28g; eggs: 50g; nuts: 43g; seeds: 28g; legumes: 113g; fats and oils: 15g.  

*AHEI*
1. Vegetable
2. Fruits
3. Nuts and legumes
4. Red/processed meat
5. Alcohol
6. SSB/Juice
7. EPA and DHA
8. PUFA
9. Sodium
10. Fibre

Serving size: vegetables and fruit: 80g; nuts and dry beans: 28g; legumes: 113g; meat: 113g. Potatoes did not count as vegetables. For alcohol components, nondrinkers received a score of 2.5. Since few women consumed alcohol in the SWHS, women who drank received a score of 5 and standards showing were for men.

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
